\section{Related Work}
\label{sec:related}

Nikolaenko, et al., \cite{nikolaenko2013privacy} proposed a scalable
privacy-preserving system for ridge-regression combining additive homomorphic
encryption and Yao's garbled circuits.  In their setting, a single evaluator is
interested in learning ridge regression over data of a large number of data
owners without learning the individual data of data owners. Our setting and
approach is different: (\emph{a.}) we don't want to reveal output to the
evaluator, (\emph{b.}) we have multiple subscribers who want the output of
computation, (\emph{c.}) our data owners, publishers, are oblivious of
subscribers and subscribers are oblivious of publishers, (\emph{d.}) we support
arbitrary polynomial-time computations as opposed to just ridge regression, and
(\emph{e.}) we don't necessarily need a third party \garbler, as shown in
Figure~\ref{fig:pps-local} if a set of subscribers controlled by a single
entity can do a modest amount of computation. Nikolaenko, et
al.,\cite{nikolaenko2013privacy} proposed a similar system but for
privacy-preserving matrix factoring as opposed to ridge regression.

Naveed, et al., \cite{naveed2014controlled} proposed a new primitive called
controlled functional encryption inspired by functional encryption. Instead of
using the same key for computing the function over multiple ciphertexts,
controlled functional encryption requires a fresh function key for every
ciphertext. They construct an efficient controlled functional encryption scheme
for arbitrary polynomial-time computations based on Yao's garbled circuits and
CCA2 secure public key encryption. Their setting involves a data owner who
wants a client to perform only certain computations on its data with the help
of an online key authority. Their setting is similar to our setting of
Figure~\ref{fig:pps-local}; however, in our setting publishers and subscribers
are oblivious to each other.

Fully homomorphic encryption allows arbitrary computation on encrypted data.
Gentry proposed the first fully homomorphic encryption
scheme \cite{brakerski2011fully,gentry2009fully} followed by several
improved schemes, e.g., Brakerski, et al., BGV scheme
\cite{brakerski2014leveled}. Dijk, et al., \cite{van2010impossibility}
showed that privacy-preserving outsourced computation on data from multiple
parties and supplying output to multiple parties, our setting, requires, in
addition to fully homomorphic encryption, access-controlled ciphertexts and
re-encryption. They reduce a scheme that computes on data from two parties
and supply the output to two parties to black box program obfuscation, which
is impossible in general \cite{barak2001possibility}.
